---
title: "Challenge 7"
author: "HAN YIYI"
date: "2023-10-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# I. All about ggplot2

### 1. Palmer Penguins: Plot Creation

```{r, eval=TRUE,echo=TRUE}
library(tidyverse)
library(palmerpenguins)
glimpse(penguins)

#start with data frame
ggplot(data = penguins,
#map bill depth to x axis
       mapping = aes(x = bill_depth_mm,
#map bill length to y axis
                     y = bill_length_mm,
#Map species to the color of each point
                     colour = species)) + 
#Represent each observation with a point
  geom_point() +
#Title the plot
  labs(title = "Bill depth and length",
#Add a subtitle
       subtitle = "Dimensions for Adelie, Chinstrap, and Gentoo Penguins",
#Label x axis and y axis
       x = "Bill depth (mm)", y = "Bill length (mm)",
#Label the legend "Species"
       colour = "Species",
#Add a caption for data source
       caption = "Source: Palmer Station LTER / palmerpenguins package") +
#Use a discrete colour scale that is designed to be perceived by viewers with common forms of colour blindness
  scale_color_viridis_d()

```
<br>

### 2. Aesthetic options: Color

```{r, eval=TRUE,echo=TRUE}
ggplot(penguins) + aes(x = bill_depth_mm, y = bill_length_mm,
           colour = species) + ##Map species to the color of each point
            geom_point() + scale_colour_viridis_d()
```
<br>

### 3. Aesthetic options: Shape
```{r, eval=TRUE,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, colour = species, shape = island)) + #Map island to the shape of each point
geom_point() + scale_colour_viridis_d()
```
<br>
```{r, eval=TRUE,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, colour = species, shape = species)) + ##Map species to the shape of each point
geom_point() + scale_colour_viridis_d()
```
<br>

### 4. Aesthetic options: Size
```{r, eval=TRUE,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, colour = species, shape = species, #Map species to the shape of each point
size = body_mass_g)) + #Map body_mass_g to the size of each point
geom_point() + scale_colour_viridis_d()
```
<br>

### 5. Aesthetic options: Alpha/Transparency
```{r, eval=TRUE,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, colour = species,
shape = species, size = body_mass_g, alpha = flipper_length_mm)) +
#map flipper_length_mm to the transparency of each point
geom_point() + scale_colour_viridis_d()
```
<br>

### 6. Mapping vs. Setting
```{r, eval=TRUE,echo=TRUE}
#Mapping
ggplot(penguins) +
aes(x = bill_depth_mm,
y = bill_length_mm,
size = body_mass_g,
alpha = flipper_length_mm) +
geom_point()
```
<br>
```{r, eval=TRUE,echo=TRUE}
#Setting
ggplot(penguins) +
aes(x = bill_depth_mm,
y = bill_length_mm) +
geom_point(size = 2, alpha = 0.5)
```
<br>

### 7. Faceting: species-island
```{r, eval=TRUE,echo=TRUE}
ggplot(penguins) +
aes(x = bill_depth_mm,
y = bill_length_mm) +
geom_point() +
facet_grid(species ~ island)
```
<br>

### 8. Faceting: species-sex
```{r, eval=TRUE,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
facet_grid(species ~ sex)
```
<br>

### 9. Faceting: sex-species
```{r, eval=TRUE,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
facet_grid(sex ~ species)
```
<br>

### 10. Faceting: -species
```{r, eval=TRUE,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
facet_wrap(~ species)
```
<br>

### 11. Faceting: put in two columns
```{r, eval=TRUE,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
facet_wrap(~ species, ncol = 2)
```
<br>

### 12. Faceting: - species
```{r, eval=TRUE,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
facet_grid(. ~ species)
```
<br> 

### 13. Faceting: add colors
```{r, eval=TRUE,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, color = species)) +
geom_point() + facet_grid(species ~ sex) + scale_color_viridis_d()
```
<br>

### 14. Faceting: color, no legend
```{r, eval=TRUE,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, color = species)) +
geom_point() + facet_grid(species ~ sex) + scale_color_viridis_d() +
guides(color = "none")
```
<br>

# II. Visualizing numeric variables

### 1. Glimpse at the Data
```{r, eval=TRUE,echo=TRUE}
library(openintro)
glimpse(loans_full_schema)

loans <- loans_full_schema %>%
select(loan_amount, interest_rate, term, grade,
state, annual_income, homeownership, debt_to_income)
glimpse(loans)
```
<br>

### 2. Histogram
```{r, eval=TRUE,echo=TRUE}
library(tidyverse)
ggplot(loans) + aes(x = loan_amount) +
geom_histogram()
```
<br>

### 3. Hisrogram: change binwidth
```{r, eval=TRUE,echo=TRUE}
# change binwidth to 1000
ggplot(loans, aes(x = loan_amount)) +
geom_histogram(binwidth = 1000)
```
<br>
```{r, eval=TRUE,echo=TRUE}
#change binwidth to 5000
ggplot(loans, aes(x = loan_amount)) +
geom_histogram(binwidth = 5000)
```
<br>
```{r, eval=TRUE,echo=TRUE}
#change binwidth to 20000
ggplot(loans, aes(x = loan_amount)) +
geom_histogram(binwidth = 20000)
```
<br>

### 4. Customizing histograms
```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = loan_amount)) + geom_histogram(binwidth = 5000) +
labs(x = "Loan amount ($)", y = "Frequency", title = "Amounts of Lending Club loans" )
```
<br>

### 5. Fill with a categorical variable
```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = loan_amount, fill = homeownership)) +
geom_histogram(binwidth = 5000, alpha = 0.5) +
labs(x = "Loan amount ($)",y = "Frequency",title = "Amounts of Lending Club loans")
```
<br>

### 6. Facet with a categorical variable
```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = loan_amount, fill = homeownership)) + geom_histogram(binwidth = 5000) +
labs(x = "Loan amount ($)",y = "Frequency",title = "Amounts of Lending Club loans") +
facet_wrap(~ homeownership, nrow = 3)
```
<br>

### 7. Density plot
```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = loan_amount)) +
geom_density()
```
<br>

### 8. Density plot: adjusting binwidth
```{r, eval=TRUE,echo=TRUE}
# change binwidth to 0.5
ggplot(loans, aes(x = loan_amount)) +
geom_density(adjust = 0.5)
```
<br>
```{r, eval=TRUE,echo=TRUE}
# change binwidth to 1 (default)
ggplot(loans, aes(x = loan_amount)) +
geom_density(adjust = 1)
```
<br>
```{r, eval=TRUE,echo=TRUE}
# change binwidth to 2
ggplot(loans, aes(x = loan_amount)) +
geom_density(adjust = 2)
```
<br>

### 9. Customizing density plots
```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = loan_amount)) +
geom_density(adjust = 2) +
labs( x = "Loan amount ($)", y = "Density", title = "Amounts of Lending Club loans" )
```
<br>

### 10. Adding a categorical variable

```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = loan_amount, fill = homeownership)) +
geom_density(adjust = 2, alpha = 0.5) +
labs(x = "Loan amount ($)",y = "Density",title = "Amounts of Lending Club loans", fill = "Homeownership")
```
<br>

### 11. Box plot
```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = interest_rate)) +
geom_boxplot()
```
<br>

### 11. Box plot and outliers
```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = annual_income)) +
geom_boxplot()
```
<br>

### 12. Customizing box plots
```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = interest_rate)) +geom_boxplot() +labs(x = "Interest rate (%)",y = NULL,
title = "Interest rates of Lending Club loans") +
theme( axis.ticks.y = element_blank(), axis.text.y = element_blank() )
```
<br>

### 13. Adding a categorical variable
```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = interest_rate,
y = grade)) +
geom_boxplot() +
labs(x = "Interest rate (%)",y = "Grade",title = "Interest rates of Lending Club loans",subtitle = "by grade of loan")
```
<br>

### 14. Scatter plot
```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = debt_to_income, y = interest_rate)) +
geom_point()
```
<br>

### 14. Hex plot
```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = debt_to_income, y = interest_rate)) +
geom_hex()
```
<br>

### 15. Applying filter to hex plot
```{r, eval=TRUE,echo=TRUE}
ggplot(loans %>% filter(debt_to_income < 100),
aes(x = debt_to_income, y = interest_rate)) +
geom_hex()
```
<br>

# Visualizing categoric variables

### 1. Bar plot
```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = homeownership)) +
geom_bar()
```
<br>

### 2. Segmented bar plot
```{r, eval=TRUE,echo=TRUE}
#create segments within the bars
ggplot(loans, aes(x = homeownership,
fill = grade)) +
geom_bar()
```
<br>

### 3. Make bar plot on the same level
```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = homeownership, fill = grade)) +
#make plot on the same level
geom_bar(position = "fill")
```
<br>

### 4. Customizing the bar plot
```{r, eval=TRUE,echo=TRUE}
#switch x axis and y axis
ggplot(loans, aes(y = homeownership, fill = grade)) + geom_bar(position = "fill") +
labs( x = "Proportion", y = "Homeownership", fill = "Grade", title = "Grades of Lending Club loans", subtitle = "and homeownership of lendee")
```
<br>

# IV. Visualizing variables of varied types

### 1. Violin plots
```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = homeownership, y = loan_amount)) +
geom_violin()
```
<br>

### 2. Ridge plots
```{r, eval=TRUE,echo=TRUE}
library(ggridges)
ggplot(loans, aes(x = loan_amount, y = grade, fill = grade, color = grade)) +
geom_density_ridges(alpha = 0.5)

```
<br>
